---
title: "nottshcData package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Template Function Skeleton}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  echo = TRUE
)
```

# Background

The CDU Data Science Team are using and building a R package called {nottshcData} that uses get_ and tidy_ functions to get data from a SQL data warehouse in a consistent way. Each table used in the data warehouse has corresponding functions but there are also functions for calculations. More was written about it by Milan Wiedemannon the [team blog](https://cdu-data-science-team.github.io/team-blog/posts/2021-08-06-nottshcverse/).

The following code snippets are related to the files needed to connect to SQL servers and the message file upon connection. These files must be incorporated into a package to work.

# Creating new SQL connections

Add details to files `connect_sql.R` 

```{r connect-sql}
#' Connect to SQL servers
#'
#' @param driver String, specifying driver
#' @param server String, specifying server, get overwritten at the moment,
#' might need to revisit this functionality at some point later
#' @param database String, specifying database ("database1", "database2",
#' "database3", "database3", "server2")
#'
#' @section Last updated by:
#' Person
#' @section Last updated date:
#' yyyy-mm-dd
#'
#' @return
#' @export
connect_sql <- function(driver = "SQL Server",
                        server = c(
                          "server1",
                          "server2"
                        ),
                        database = c(
                          "database1",
                          "database2",
                          "database3",
                          "database4",
                          "database5",
                          "databaseA" # From server2
                        )) {

  # check server and database argument
  server <- match.arg(server)
  database <- match.arg(database)

  # this logic defines the server for a given database

  if (database %in% c(
    "database1",
    "database2",
    "database3",
    "database4",
    "database5"
  )) {
    server <- "server1"
  }

  if (database == "databaseA") {
    server <- "server2"
  }

  conn <- try(pool::dbPool(
    drv = odbc::odbc(),
    driver = driver,
    server = server,
    database = database,
    trusted_connection = TRUE
  ))

  if ("try-error" %in% class(conn)) {
    cli::cli_div(theme = list(span.emph = list(color = "red")))
    cli::cli_h1("Connecting to {driver}")
    cli::cli_alert_danger("Failed to connect to database: {.emph {database}}")
    cli::cli_alert_info("Check your VPN connection and whether you have access to the database.")
    cli::cli_end()
  } else {
    cli::cli_div(theme = list(span.emph = list(color = "green")))
    cli::cli_h1("Connecting to {driver}")
    cli::cli_alert_success("Connecting to database: {.emph {database}}")
    cli::cli_end()

    conn
  }
}
```

Add to the message file `zzz.R`.

```{r zzz}

.onAttach <- function(libname, pkgname) {
  version <- read.dcf(
    file = system.file("DESCRIPTION", package = pkgname),
    fields = "Version"
  )

  cli::cli_text(paste0("This is ", pkgname, " ", version))
  cli::cli_text(paste0(pkgname, " is currently in development -
                       please report any bugs or ideas at:"))
  cli::cli_text("https://github.com/CDU-data-science-team/<Repo>/issues")

  cli::cli_h1("Connecting to NOTTSHC servers:")
  cli::cli_alert_info('conn_sql_database1 <- connect_sql(database = "database1")')
  cli::cli_alert_info('conn_sql_database2 <- connect_sql(database = "database2")')
  cli::cli_alert_info('conn_sql_database3 <- connect_sql(database = "database3")')
  cli::cli_alert_info('conn_sql_database4 <- connect_sql(database = "database4")')
  cli::cli_alert_info('conn_sql_database5 <- connect_sql(database = "database5")')
  cli::cli_alert_info('conn_sql_database16 <- connect_sql(database = "database6")')
  cli::cli_alert_info('conn_sql_databaseA <- connect_sql(database = "databaseA")')
  cli::cli_alert_info('conn_mysql_database_fft <- connect_mysql(database = "database_fft")')
}

```

