---
title: "Template Function Skeleton"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Template Function Skeleton}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  echo = TRUE
)
```

# Background

The CDU Data Science Team are using and building a R package called {nottshcData} that uses get_ and tidy_ functions to get data from a SQL data warehouse in a consistent way. Each table used in the data warehouse has corresponding functions but there are also functions for calculations. More was written about it by Milan Wiedemannon the [team blog](https://cdu-data-science-team.github.io/team-blog/posts/2021-08-06-nottshcverse/).

The following code snippets are related to the files needed to connect to SQL servers and the message file upon connection. These files must be incorporated into a package to work.

Note where <> is used this is for areas where code needs to be updated.

# Create get function - using table name

The only different between this and the next get_ function is the code for the SQL. For this function the SQL code is the simplest:

```{r get-sql}

# Title section header ----
#' Get table description
#' @description Template links to \code{\link{tidy_db_tbl}}
#'
#' @param from String, specifying start date in "YYYY-MM-DD" format
#' (Variable: StartDateTime)
#' @param to String, specifying end date in "YYYY-MM-DD" format
#' (Variable: StartDateTime)
#' @param select_vars Logical, specifying whether to include only selected
#' variables (TRUE)
#' or all variables from the database (FALSE).
#' @param conn A database connection
#' @param return String, specifying whether to return a "tbl_sql" connection
#' or "tbl_df"
#'
#' @section Last updated by:
#' Template
#' @section Last updated date:
#' yyyy-mm-dd
#'
#' @return String/Dataframe A SQL connection or a data frame
#' @export
get_db_tbl <- function(from = NULL,
                       to = NULL,
                       select_vars = TRUE,
                       conn = conn_sql_database1,
                       return = c("tbl_sql", "tbl_df")) {
  
  cli::cli_text("This table is not currently in <Schema>")

  # Check function arguments
  return <- match.arg(return)
  # Create connection to server
  if (!exists("conn_sql_database1")) {
    assign("conn_sql_database1",
      connect_sql(database = "database1"),
      envir = globalenv()
    )
  }

  # Create connection to table
  db_data <- dplyr::tbl(
    conn,
    dbplyr::in_schema(
      "<SCHEMA>",
      "<table>")

  )
  
  # Filter date range
  if (!is.null(from)) {
    db_data <- db_data %>%
      dplyr::filter(as.Date(StartDateTime) >= from)
  }

  if (!is.null(to)) {
    db_data <- db_data %>%
      dplyr::filter(as.Date(StartDateTime) <= to)
  }

  # Select or deselect variables
  if (select_vars) {
    db_data <- db_data %>%
      dplyr::select(-Rn)
  }

  # Return
  if (return == "tbl_sql") {
    db_data
  } else if (return == "tbl_df") {
    db_data %>%
      dplyr::collect()
  }
}


```

# Create get function - listing columns

Some SQL tables have columns that are varchar(max), nvarchar(max) or binary and to get around this they need to be listed at the [end of a SQL SELECT statement]() and the code is slightly different:

```{r sql-listed-columns}

# Title section header ----
#' Get table description
#' @description Template links to \code{\link{tidy_db_tbl}}
#'
#' @param from String, specifying start date in "YYYY-MM-DD" format
#' (Variable: StartDateTime)
#' @param to String, specifying end date in "YYYY-MM-DD" format
#' (Variable: StartDateTime)
#' @param select_vars Logical, specifying whether to include only selected
#' variables (TRUE)
#' or all variables from the database (FALSE).
#' @param conn A database connection
#' @param return String, specifying whether to return a "tbl_sql" connection
#' or "tbl_df"
#'
#' @section Last updated by:
#' Template
#' @section Last updated date:
#' yyyy-mm-dd
#'
#' @return String/Dataframe A SQL connection or a data frame
#' @export
get_db_tbl <- function(from = NULL,
                       to = NULL,
                       select_vars = TRUE,
                       conn = conn_sql_database1,
                       return = c("tbl_sql", "tbl_df")) {
  
  cli::cli_text("This table is not currently in REPORT_BASE")

  # Check function arguments
  return <- match.arg(return)
  # Create connection to server
  if (!exists("conn_sql_database1")) {
    assign("conn_sql_database1",
      connect_sql(database = "database1"),
      envir = globalenv()
    )
  }

  db_data <- dplyr::tbl(conn, dbplyr::sql(
    "SELECT <Columns>
    <Any varchar(max) at end>
  FROM <Schema>.<Table>
    "
  ))
  
  # Filter date range
  if (!is.null(from)) {
    db_data <- db_data %>%
      dplyr::filter(as.Date(StartDateTime) >= from)
  }

  if (!is.null(to)) {
    db_data <- db_data %>%
      dplyr::filter(as.Date(StartDateTime) <= to)
  }

  # Select or deselect variables
  if (select_vars) {
    db_data <- db_data %>%
      dplyr::select(-Rn)
  }

  # Return
  if (return == "tbl_sql") {
    db_data
  } else if (return == "tbl_df") {
    df_data <- db_data %>%
      dplyr::collect()
    df_data
  }
}


```

# Create tidy function

The tidy function has all the tidying data code. Note that the order of the parameters/arguments needs to be with SQL first with the final code for tidying column names to come last so that parameters/arguments work both on SQL and R code:

```{r eval=FALSE}

#' Tidy table
#'
#' @description Template
#' @param data tbl_df from \code{\link{get_db_tbl}}
#' @param tidy_names Logical, specifying whether to rename variables to be
#' consistent across different tables
#'
#' @section Last updated by:
#' Template
#' @section Last updated date:
#' yyyy-dd-mm
#'
#' @return
#' @export
tidy_db_tbl <- function(data,
                        tidy_names = TRUE) {
  if (tidy_names) {
    data <- dplyr::rename_all(data, janitor::make_clean_names) %>% 
      dplyr::rename(
      new_name = old_name
    ) 

  }

  data
}


```
